Lentiptical galaxies and their ordinary black holes

### 2015-07-22 papers/lentiptical/lentiptical.tex
wed

Title: Lentiptical galaxies and their extraordinarily ordinary black holes \\
Authors: G. A. D. Savorgnan and A. W. Graham \\
Affiliation: Centre for Astrophysics and Supercomputing, Swinburne University of Technology, Hawthorn, Victoria 3122, Australia. \\

\begin{abstract}
Early-type galaxies include elliptical and lenticular galaxies. 
%Most early-type galaxies are made of two principal components [ref krajnovic]: 
%a spheroid (or bulge) of stars, with an approximately ellipsoidal shape, 
%and a relatively flat stellar disk. 
%Elliptical galaxies are said to have no stellar disk, 
%whereas lenticular galaxies are composed of a central bulge of stars encased in a larger stellar disk. 
Lenticular galaxies are composed of a central spheroid (or bulge) of stars encased in a larger stellar disk. 
When perfoming bulge/disk decomposition, 
the spheroidal component is typically described with a S\'ersic profile (ref sersic), 
while the disk is modelled with an exponential function. 
Theoretically, the bulge-to-disk ratio, 
which describes the relative importance of the spheroidal component over the disk component, 
can assume any positive value. 
However, several studies have taken into account only bulge/disk decompositions 
in which the exponential-disk function neatly dominates over the S\'ersic-spheroid profile at large galaxy radii, 
and rejected those decompositions in which the exponential-disk function remains ``embedded'' within the S\'ersic-spheroid profile, 
considering such decompositions as unphysical.
Here we show that these ``rejected'' models correctly reproduce the photometric and kinematic properties of a class of early-type galaxies, 
intermediate between elliptical and lenticular galaxies, that we name \emph{lentiptical}. 
Lentiptical galaxies have often been confused with lenticular galaxies and, 
consequently, their bulge luminosities have been largely underestimated. 
This mistake has led to some wrong conclusions, 
such as the claim that a number of lentiptical galaxies (MRK 1216 [ref yldrim+2015], 
NGC 1277 [ref vdb+2012], NGC 1271 [ref walsh+2015], and NGC 1332 [ref rusli+2011]) 
host a central black hole whose mass is abnormally large 
compared to expectations from its (underestimated) bulge luminosity.
When lentiptical galaxies are modelled according to our simple prescription, 
which uses the lowest number of free parameters, 
they no longer appear as extreme outliers in the (black hole mass) -- (spheroid stellar mass) diagram. 
Previous ``anomalies'' are explained by one simple ``rule'' 
and no need di avere nuovi scenari

%Our results demonstrate that there is no bimodality in the distribution of the bulgetodisk
%that the claimed bimodality is artificial

%we show that the ell profile is enough to estabilish if the disk is embedded or not

%Lentiptical galaxies are an intermediate class of galaxies between elliptical  
%and lenticular galaxies.
%Lentipticals are early-type, bulge-dominated galaxies that feature a fast-rotating, 
%intermediate-scale disk of stars embedded within a slow-rotating spheroid of stars.
%Such spheroid dominates the light in the central region of the galaxy and also at large radii, 
%unlike lenticular galaxies, whose bulge is encased within a (more extended) large-scale disk. 
\end{abstract}

>>>>

Title: Lentiptical galaxies and their non-extraordinary black holes \\
Authors: Giulia A. D. Savorgnan and Alister W. Graham \\
Affiliation: Centre for Astrophysics and Supercomputing, Swinburne University of Technology, Hawthorn, Victoria 3122, Australia. \\

\begin{abstract}
Early-type galaxies include elliptical and lenticular galaxies. 
%Most early-type galaxies are made of two principal components [ref krajnovic]: 
%a spheroid (or bulge) of stars, with an approximately ellipsoidal shape, 
%and a relatively flat stellar disk. 
%Elliptical galaxies are said to have no stellar disk, 
%whereas lenticular galaxies are composed of a central bulge of stars encased in a larger stellar disk. 
Lenticular galaxies are composed of a central spheroid (or bulge) of stars encased in a larger stellar disk. 
When perfoming bulge/disk decomposition, 
the spheroidal component is typically described with a S\'ersic profile (ref sersic), 
while the disk is modelled with an exponential function. 
Theoretically, the bulge-to-disk ratio, 
which describes the relative importance of the spheroidal component over the disk component, 
can assume any positive value. 
However, several studies [ref] have taken into account only bulge/disk decompositions 
in which the exponential-disk function neatly dominates over the S\'ersic-spheroid profile at large galaxy radii, 
and rejected those decompositions in which the exponential-disk function remains ``embedded'' within the S\'ersic-spheroid profile, 
considering such decompositions as unphysical.
Here we show that these ``rejected'' models correctly reproduce the photometric and kinematic properties of a class of early-type galaxies, 
intermediate between elliptical and lenticular galaxies, that we name \emph{lentiptical}. 
Lentiptical galaxies have often been confused with lenticular galaxies and, 
consequently, their bulge luminosities have been largely underestimated. 
This mistake has led to some wrong conclusions, 
such as the claim that a number of lentiptical galaxies (MRK 1216 [ref yldrim+2015], 
NGC 1277 [ref vdb+2012], NGC 1271 [ref walsh+2015], and NGC 1332 [ref rusli+2011]) 
host a central black hole whose mass is abnormally large 
compared to expectations from its (underestimated) bulge luminosity.
When lentiptical galaxies are modelled according to our simple prescription, 
which uses the lowest number of free parameters, 
they no longer appear as extreme outliers in the (black hole mass) -- (spheroid stellar mass) diagram. 
Previous ``anomalies'' are explained and eliminated by one simple ``rule''. 
This nullifies the need of invoking different evolutionary scenarios 
for these galaxies and their non-extraordinary black holes.

%Our results demonstrate that there is no bimodality in the distribution of the bulgetodisk
%that the claimed bimodality is artificial
%we show that the ell profile is enough to estabilish if the disk is embedded or not
%Lentiptical galaxies are an intermediate class of galaxies between elliptical  
%and lenticular galaxies.
%Lentipticals are early-type, bulge-dominated galaxies that feature a fast-rotating, 
%intermediate-scale disk of stars embedded within a slow-rotating spheroid of stars.
%Such spheroid dominates the light in the central region of the galaxy and also at large radii, 
%unlike lenticular galaxies, whose bulge is encased within a (more extended) large-scale disk. 
\end{abstract}
